Untitled

### 2016-11-22 Code/Explore_unaggregate_data.Rmd
Create AL cut of unaggregated dataset

```{r load datasets}
dat.male <- read.table("/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/males_export.txt", header = T, sep="\t", na.strings = " ")
names(dat.male) <- c("State", "Age", "Sex", "Race", "COD", "Year", "Crude_Rate", "Count", "Population")
prop.table(table(is.na(dat.male$Count)))
head(dat.male)
table(dat.male$Sex)
str(dat.male) #note all numeric or int

dat.female <- read.table("/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/female_export.txt", header = T, sep="\t", na.strings = " ")
names(dat.female) <- c("State", "Age", "Sex", "Race", "COD", "Year", "Crude_Rate", "Count", "Population")
table(dat.female$Sex)
dat.female$Sex <- 1
str(dat.male) #note all numeric or int

@@

dim(dat.both)
dat.both <- merge(dat.both, cod.dict, by = "COD2") #to add on COD_num and cod_cat
dim(dat.both)

```

```{r for_merge}

years0610 <- dat.both[dat.both$Year3 >= 2006 & dat.both$Year3 <= 2010 & dat.both$agegrp > 1, ] 
#added the age restriction because don't want to deal with the differences in age definition right now

@@

together <- merge(years0610, not.suppressed, by = c("stabbrs", "Year3", "Sex", "Race", "agegrp", "COD_full"))

```

@@

View(together[together$rel_diff_pop > 0.6, ])
```
From above we see that the death counts match exactly and when the original count is NA the non-suppressed count is between 1 and 9.
For some reason there is some discrpancy in the populational denominators. These do not match exactly and I don't know why.

>>>>

```{r load datasets}
#loading in the data from NCHS, which supresses death counts between 1 and 9.
dat.male <- read.table("/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/males_export.txt", header = T, sep="\t", na.strings = " ")
names(dat.male) <- c("State", "Age", "Sex", "Race", "COD", "Year", "Crude_Rate", "Count", "Population")
prop.table(table(is.na(dat.male$Count)))
head(dat.male)
table(dat.male$Sex)
str(dat.male) #note all varinables are numeric or integer

dat.female <- read.table("/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/female_export.txt", header = T, sep="\t", na.strings = " ")
names(dat.female) <- c("State", "Age", "Sex", "Race", "COD", "Year", "Crude_Rate", "Count", "Population")
table(dat.female$Sex)
dat.female$Sex <- 1
str(dat.male) #note all varinables are numeric or integer

@@

dim(dat.both)
dat.both <- merge(dat.both, cod.dict, by = "COD2") #to add on COD_num and cod_cat
dim(dat.both)
```

```{r for_merge}
years0610 <- dat.both[dat.both$Year3 >= 2006 & dat.both$Year3 <= 2010 & dat.both$agegrp > 1, ] 
#added the age restriction because don't want to deal with the differences in age definition right now

@@

together <- merge(years0610, not.suppressed, by = c("stabbrs", "Year3", "Sex", "Race", "agegrp", "COD_full"))
```

@@

View(together[together$rel_diff_pop > 0.6, ])
```
From above we see that the death counts match exactly and when the original count is NA the non-suppressed count is between 1 and 9.
For some reason there is some discrepancy in the population denominators. These do not match exactly and I don't know why.
